Towards understanding the central limit theorem by learning Python basics

### 2022-05-04 paper/article.tex
Some grammatical improvements

In our paper we propose a radical way, or at least an extension of the classic way, how
basics of elementary probability theory should be taught. It is \textit{programming}.
Our conjecture is that understanding will be significantly improved if the main concepts
of probability theory are supported with simple computer programs. The output for their flexible input
should be immediately checked, eventually in a web browser, and by changing the input parameters
to a higher number, the results can be quickly generalized. We emphasize that computers
can take on the high number of computatations from human---and this is what we exactly want.
A quite simple \textit{sample space} can contain \textit{a lot} of elements, even millions or more, and it cannot
be expected that non-experts can count their elements without deeper knowledge. In fact,
experts in probability are usually experts in combinatorics as well. To reach a reasonable
level of understanding of the main concepts in probability, by using just paper and pencil,
one needs to have a very strong and \textit{safe} background in combinatorics.

@@

Why did we choose Python as the programming language for this course?
There are a couple of reasons we would like to note. First of all: It is
free, independent of the used operating system, has good documentation
and great tutorials. In addition, Python is currently a very popular
programming language: according to
\url{https://madnight.github.io/githut/#/pull_requests/2020/4}, Python
was the second most popular language on GitHub in the 4th quarter of 2020;
moreover, ZDNet's recent article \cite{LiamTung2020} highlights that Python
was the second best popular language in November 2020.
Many programming courses teach it as a first
programming language because of its ease of use and short expressive
code.

@@

On the other hand, in the field of data science
Python is currently the mostly used programming language. Especially in
machine learning, which could be seen as an advanced application of
probability, Python is very popular. We think that students who believe
that the exercises they solve are not artificially constructed for the
course, but have some connection to the real world, will be more
motivated. As a teacher we can give students the impression that if they
use Python in their introductory course on probability, they take a first
step into the prestigious field of data science. This may increase the
motivation of students and as a result they will achieve a higher level.

@@

\item Modify the program on line 7 and 14 in order to solve this problem:
\begin{quote}
Alice und Bob roll a die four times consecutively.
If the sum of the outcomes is between 7 and 14, Alice wins, otherwise Bob.
For which player is the game advantageous?
\end{quote}

@@

Fig.~\ref{42} shows a solution by a student for question 3. It is clear that this
student successfully combined previous programming knowledge, theory and praxis. Similarly,
two other students found the same idea to change the limits to have $7\leq X(\omega)\leq14$,
and one of them tried several attempts to find better limits---without success.
(Note that for an even number of dice there is no trivial solution by halving the
sample space symmetrically in the middle. So, in some sense, question 3 is adequate to motivate
experimenting.)

@@

We are thankful to the students Alexander, Romana, Sandra and Sarah
for their participation in the project, and to Andreas Lindner who
gave us useful feedback on the first version of the manuscript.

>>>>

In our paper we propose a radical way, or at least an extension of the classic way, how
basics of elementary probability theory should be taught. It is \textit{programming}.
Our conjecture is that understanding will be significantly improved if the main concepts
of probability theory are supported with simple computer programs. The output for their flexible input
should be immediately checked, eventually in a web browser, and by changing the input parameters
to a higher number, the results can be quickly generalized. We emphasize that computers
can take on the high number of computations from human---and this is what we exactly want.
A quite simple \textit{sample space} can contain \textit{a lot} of elements, even millions or more, and it cannot
be expected that non-experts can count their elements without deeper knowledge. In fact,
experts in probability are usually experts in combinatorics as well. To reach a reasonable
level of understanding of the main concepts in probability, by using just paper and pencil,
one needs to have a very strong and \textit{safe} background in combinatorics.

@@

Why did we choose Python as the programming language for this course?
There are a couple of reasons we would like to note. First of all: It is
free, independent of the used operating system, has good documentation
and great tutorials. In addition, Python is currently a very popular
programming language: according to
\url{https://madnight.github.io/githut/#/pull_requests/2020/4}, Python
was the second most favoured language on GitHub in the 4th quarter of 2020;
moreover, ZDNet's recent article \cite{LiamTung2020} highlights that Python
was the second best liked language in November 2020.
Many programming courses teach it as a first
programming language because of its ease of use and short expressive
code.

@@

On the other hand, in the field of data science
Python is currently the mostly used programming language. Especially in
machine learning, which could be seen as an advanced application of
probability, Python is very well liked. We think that students who believe
that the exercises they solve are not artificially constructed for the
course, but have some connection to the real world, will be more
motivated. As a teacher we can give students the impression that if they
use Python in their introductory course on probability, they take a first
step into the prestigious field of data science. This may increase the
motivation of students and as a result they will achieve a higher level.

@@

\item Modify the program on line 7 and 14 in order to solve this problem:
\begin{quote}
Alice and Bob roll a die four times consecutively.
If the sum of the outcomes is between 7 and 14, Alice wins, otherwise Bob.
For which player is the game advantageous?
\end{quote}

@@

Fig.~\ref{42} shows a solution by a student for question 3. It is clear that this
student successfully combined previous programming knowledge, theory and practise. Similarly,
two other students found the same idea to change the limits to have $7\leq X(\omega)\leq14$,
and one of them tried several attempts to find better limits---without success.
(Note that for an even number of dice there is no trivial solution by halving the
sample space symmetrically in the middle. So, in some sense, question 3 is adequate to motivate
experimenting.)

@@

We are thankful to the students Alexander, Romana, Sandra and Sarah
for their participation in the project, and to Andreas Lindner
and two anonymous reviewers who
gave us useful feedback on the first versions of the manuscript.
